Static contract checking for Haskell

### 2011-08-23 paper.tex
Add ruleform macro and use it in Fig 6
Paper update BNF

\begin{figure}
 \begin{center}
  \[  \begin{array}{rcl}
    \etrans{\mbox{expression}} &\to& t~(\mbox{Term}) \\
    \dtrans{f~\vec{x} = \dots} &\to& \Phi~(\mbox{Set of formulae}) \\
    \ktrans{\mbox{data } T = \dots} &\to& \Phi~(\mbox{Set of formulae}) \\
    \ctrans{f \in c} &\to& \Phi~(\mbox{Set of formulae}) \\
  \end{array} \]
  \end{center}
  \caption{Translations}
  \label{trans}
\end{figure}

@@

\subsection{$\dtrans{}$ -- Definitions}
We give in figure~\ref{dtrans-reg} and figure~\ref{dtrans-case} the two translations
of function definitions.

@@

Translating definitions that use pattern-matching is more challenging
and is described in figure~\ref{dtrans-case}.

@@

\begin{figure}
 $$\dtrans{f(\vec{x}) = e}$$
  $$ \forall \vec{x},y.~ \min{y} \land y = f(\vec{x}) \to y = \etrans{e}$$
  \caption{$\dtrans{}$ -- Regular definitions}
  \label{dtrans-reg}
\end{figure}

\begin{figure*}
 $$ \dtrans{f(x_1,\dots,x_n) = \mbox{case } e \mbox{ of } [K_1(\vec{x_1}) = e_1,\dots,K_n(\vec{x_n}) = e_n]}$$
 \begin{center}
   \[  \begin{array}{rclcl}
     \forall \vec{a},y.~\mbox{min}(y) \land f(\vec{a}) = y &\rightarrow&
     \multicolumn{3}{c}{  \texttt{min}(e) \land (e = \texttt{BAD} \lor
       \bigvee_i \forall \vec{x}.~e = K_i(\vec{x}) \lor y = \texttt{UNR})} \\
     &\land& \forall \vec{x_1}.~\etrans{e} = K_1(\vec{x_1}) &\to& y = \etrans{e_1} \\
     &\land& & \cdots & \\
     &\land& \forall \vec{x_n}.~\etrans{e} = K_n(\vec{x_n}) &\to& y = \etrans{e_n}) \\
   \end{array} \]
 \end{center}
 \caption{$\dtrans{}$ -- Case definitions}
 \label{dtrans-case}
\end{figure*}

@@

\begin{figure*}
 $$\ktrans{\mbox{data } T = K_1, \dots, K_n} = \Phi_1 \cup \Phi_2 \cup \Phi_3 \cup \Phi_4$$
  where
  \begin{center}
    \[  \begin{array}{rcl}
      \Phi_1 &=& \bigcup_{1 \leq i \leq n}~\forall \vec{x},a.~(\min{a} \land K_i(\vec{x}) = a) \to \bigwedge_{1 \leq j \leq k} x_j = sel_{j,K_i}(a) \\
      \Phi_2 &=& \bigcup_{1 \leq i < j \leq n}~\forall \vec{x},\vec{y},a.~ \lnot (\min{a} \land K_i(\vec{x}) = a \land K_j(\vec{x}) = a) \\
      \Phi_3 &=& \bigcup_{1 \leq i \leq n}~\forall \vec{x},a.~\min{a} \land a = K_i(\vec{x}) \to ((\bigwedge_{1 \leq j \leq k} \cf{x_j}) \tot \cf{K_i(\vec{x})}) \\
      \Phi_4 &=& \bigcup_{1 \leq i \leq n}~\forall \vec{x},a.~(\min{a} \land a = K_i(\vec{x})) \to a \neq \unr \land a \neq \bad 
    \end{array} \]
  \end{center}
  \caption{$\ktrans{}$ -- Data type translation}
  \label{ktrans}
\end{figure*}

>>>>

\begin{figure}
 \begin{center}
  \[  \begin{array}{rcl}
    \etrans{\mbox{expression}} &\to& t~(\mbox{Term}) \\
    \dtrans{def} &\to& \Phi~(\mbox{Set of formulae}) \\
    \ktrans{\mbox{data } T = \dots} &\to& \Phi~(\mbox{Set of formulae}) \\
    \ctrans{f \in c} &\to& \Phi~(\mbox{Set of formulae}) \\
  \end{array} \]
  \end{center}
  \caption{Translations}
  \label{trans}
\end{figure}

@@

\subsection{$\dtrans{}$ -- Definitions}
We give in figure~\ref{dtrans} the two translations of function
definitions.

@@

Translating definitions that use pattern-matching is more challenging
and is described in figure~\ref{dtrans}.

@@

\begin{figure*}
\[
\begin{array}{rcl}
  \dtrans{\mbox{data } T = K_1, \dots, K_n} &=& \ktrans{\mbox{data } T = K_1, \dots, K_n} \\
  \dtrans{f \in c} &=& \ctrans{f \in c} \\
  \dtrans{f(\vec{x}) = e} &=& \forall \vec{x},y.~ \min{y} \land y =
  f(\vec{x}) \to y = \etrans{e} \\
   \raisebox{ 0.5 cm }{$\dtrans{f(x_1,\dots,x_n) = \mbox{case } e \mbox{ of } [K_i(\vec{x_i}) = e_i]}$} &\raisebox{0.5cm}{=}&  \hspace{-0.18cm} \begin{array}{rclcl}
     \forall \vec{a},y.~\mbox{min}(y) \land f(\vec{a}) = y &\rightarrow&
     \multicolumn{3}{c}{  \texttt{min}(e) \land (e = \texttt{BAD} \lor
       \bigvee_i \forall \vec{x}.~e = K_i(\vec{x}) \lor y = \texttt{UNR})} \\
     &\land& \forall \vec{x_1}.~\etrans{e} = K_1(\vec{x_1}) &\to& y = \etrans{e_1} \\
     &\land& & \cdots & \\
     &\land& \forall \vec{x_n}.~\etrans{e} = K_n(\vec{x_n}) &\to& y = \etrans{e_n}) \\
   \end{array} 
\end{array}
\]
\caption{$\dtrans{}$ -- Defintions translation}
 \label{dtrans}
\end{figure*}

@@

\begin{figure*}
 $$\ktrans{\mbox{data } T = K_1, \dots, K_n} = \Phi_1 \cup \Phi_2 \cup \Phi_3 \cup \Phi_4$$
 \hspace{5.6cm}where
  \begin{center}
    \[  \begin{array}{rcl}
      \Phi_1 &=& \bigcup_{1 \leq i \leq n}~\forall \vec{x},a.~(\min{a} \land K_i(\vec{x}) = a) \to \bigwedge_{1 \leq j \leq k} x_j = sel_{j,K_i}(a) \\
      \Phi_2 &=& \bigcup_{1 \leq i < j \leq n}~\forall \vec{x},\vec{y},a.~ \lnot (\min{a} \land K_i(\vec{x}) = a \land K_j(\vec{x}) = a) \\
      \Phi_3 &=& \bigcup_{1 \leq i \leq n}~\forall \vec{x},a.~\min{a} \land a = K_i(\vec{x}) \to ((\bigwedge_{1 \leq j \leq k} \cf{x_j}) \tot \cf{K_i(\vec{x})}) \\
      \Phi_4 &=& \bigcup_{1 \leq i \leq n}~\forall \vec{x},a.~(\min{a} \land a = K_i(\vec{x})) \to a \neq \unr \land a \neq \bad 
    \end{array} \]
  \end{center}
  \caption{$\ktrans{}$ -- Data type translation}
  \label{ktrans}
\end{figure*}
